R Notebook

### 2021-09-16 documentation_and_analysis/draftbook.Rmd
Update draftbook.Rmd
Removal of unused data
Fixed heatmap (zoom issues)

# How many electric vehicles are on the road across the UK?

@@

@@

# Transformed data
pj <- project(xy, proj4string, inverse=TRUE)
latlon <- data.frame(xy, lat=pj$y, lon=pj$x)
final <-  merge(no2_clean_row, latlon, by.x = "rowid", by.y = "rowid") %>%
  filter(year == 2019) %>% 
  select(lat, lon, no2)

```

```{r}
leaflet() %>%
  addProviderTiles("CartoDB.Positron", options = providerTileOptions(noWrap = TRUE)) %>%
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addHeatmap(data = final,
             lng = ~lon, 
             lat = ~lat, 
             intensity = ~no2,
             minOpacity = 0.05,
             max = 5,
             radius = 7)
```

>>>>

# How many electric vehicles are on the road across the UK by LA?

@@

```{r}
# Geospatial of EV Vehicles in the UK 2021 Q1
uk_ev_map %>% 
  leaflet() %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~pal(x2021_q1),
    weight = 0.1,
    opacity = 0.9, 
    color = "black",
    fillOpacity = 0.8,
    highlightOptions = highlightOptions(color = "green", weight = 2,
                                        bringToFront = TRUE),
    label = uk_ev_map_labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>% 
  addLegend(pal = pal, values = ~x2021_q1, opacity = 0.7, title = NULL,
            position = "bottomright")
```
# How many electric vehicles are on the road across the UK by LA?

```{r}
# Reading in and skipping first 5 rows
uk_ev_postcode <- read_ods(here("raw_data/ev_by_postcode.ods"), sheet = 2, skip = 6) %>% 
  rename("postcode" = "Postcode District2")
```

```{r}
# loading in shape file 
uk_shape_file_postcode <- st_read(here("raw_data/postcode_shape/EX_Sample.shp")) %>%
  clean_names() %>% 
  st_simplify(dTolerance = 1000) %>%
  st_transform("+proj=longlat +datum=WGS84") #%>% 
#  select(lad19cd, long, lat, geometry) 
```

```{r}
# Joining uk_ev + shape file 
uk_ev_map_postcode <- uk_ev_postcode %>% 
  left_join(uk_shape_file_postcode, by = c("ons_la_code_apr_2019" = "lad19cd")) %>% 
  drop_na() %>% 
  mutate(across(c(x2021_q1:x2011_q4), as.numeric)) %>% 
  st_as_sf()
```

@@

# Transformed data
pj <- project(xy, proj4string, inverse=TRUE)
latlon <- data.frame(xy, lat=pj$y, lon=pj$x)
final <-  merge(no2_clean_row, latlon, by.x = "rowid", by.y = "rowid") %>%
  filter(year == 2019) %>% 
  select(lat, lon, no2) 
```

```{r}
final <- final %>% 
  mutate(no2 = as.numeric(no2)) 
```

```{r}
bins <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
pal <- colorBin("Spectral", domain = final$no2, bins = bins, na.color = "transparent", reverse = TRUE)

leaflet() %>%
  addProviderTiles("CartoDB.Positron", options = providerTileOptions(noWrap = TRUE)) %>%
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addHeatmap(data = final,
             lng = ~lon,
             lat = ~lat,
             intensity = ~no2,
             minOpacity = 0.1,
             max = 40,
             radius = 1,
             blur = 1) %>% 
  addLegend(pal = pal, values = final$no2,
                title="Average NO2 Conc")
```

```{r}
final %>% 
  head()
```

```{r}
write_csv(final, "no2_lat_long_data.csv")
```

```{r}
no2_annual_mean <- read_ods(here("raw_data/NO2_tables.ods"), sheet = 3, skip = 2) %>% 
  clean_names()
```

```{r}
no2_annual_mean_all <- no2_annual_mean %>% 
  filter(site == "All sites") %>% 
  mutate(year = as.numeric(year))
```

```{r}
no2_annual_mean_all %>% 
  ggplot() +
  aes(x = year, y = annual_mean_no2concentration_mg_m3) + 
  geom_point() +
  geom_smooth(se = FALSE) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 70, 10), limits = c(0, 70)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  labs(x = "\nYear\n", 
       y = "\nAnnual Mean NO2 Conc mg m3\n",
       title = "\nNO2 over time in the UK\n") 
```

```{r}
library(tidyverse)
library(fable)
library(tsibble)
library(tsibbledata)
library(ggfortify)
```

```{r}
forecast_no2 <- no2_annual_mean_all %>% 
  dplyr::select(year, annual_mean_no2concentration_mg_m3) %>% 
  tsibble(index = year)
```

```{r}
autoplot(forecast_no2)
```

```{r}
fit <- forecast_no2 %>%
  model(
    mean_model = MEAN(annual_mean_no2concentration_mg_m3),
    arima = ARIMA(annual_mean_no2concentration_mg_m3)
  )
fit
```

```{r}
forecast_1 <- fit %>%
  fabletools::forecast(h = 15)
forecast_1
```

```{r}
forecast_1 %>%
  autoplot(forecast_no2) +
  ggtitle("Forecasts for Australian beer sales") +
  xlab("Year") +
  guides(colour = guide_legend(title = "Forecast"))
```
